FinalManuscript_DISCS_UG

### 2018-10-05 parts/02_relatedliterature_05partiallyhomomorphic.tex
Completed 3 of 4 cryptosystems
remaining cryptosystem is HeLib

We will then show that the cryptosystems can be modified to support limited polynomial evaluation: given an encrypted message $m$, evaluate

These operations
\subsection{The Pallier cryptosystem}
The Pallier cryptosystem \cite{stern_public-key_1999}, developed by Pascal Pallier, is a probabilistic encryption scheme which is based on the composite residuosity class problem. The scheme allows for the encryption and decryption of integer messages, and is known to be additively homomorphic. We now state the encryption and decryption algorithms of the Pallier cryptosystem and its homomorphic properties.

\subsubsection{Pallier cryptosystem description}
We first define a function $L(x)$ as the largest integer $v$ greater than zero such that $x-1 \geq vn$.
We choose two large primes $p$ and $q$, and set $n = pq, \lambda = \mathrm{lcm}(p-1,q-1)$.
Then we select an integer $g$, $0\leq g \leq n^2$ such that $\mathrm{gcd}(L(g^\lambda \bmod n^2), n) = 1$.
We denote the public key as $(g,n)$ and the private key $(p,q)$.

@@

\subsubsection{Homomorphic Properties}
The Paillier cryptosystem supports additive homomorphism as well as the multiplication of a plaintext scalar to an encrypted message. These operations are defined as follows.
For all $m_1,m_2 \in \mathbb{Z}_n$ and $k\in \mathbb{N}$, the following homomorphic properties hold.
\begin{description}
  \item[Additive homomorphism]
  \begin{align*}
    D(E(m_1)g^k\bmod n^2)=(m_1+k)\bmod n & \text{ (used to add a constant)}\\
    D(E(m_1)E(m_2)\bmod n^2)=(m_1+m_2)\bmod n & \text{ (used for binary addition)}
  \end{align*}
  \item[Multiplicative homomorphism]
  \begin{align*}
    D(E(m_1)^k\bmod n^2)= km_1\bmod n & \text{ (used to multiply a plaintext constant)}
  \end{align*}
\end{description}
In order to implement some image operations covered in this study, we require the exponentiation of ciphertexts to integer powers, i.e. we require a function $f$ so that
\begin{align*}
	D(f(E(m))) = m^k\bmod n
\end{align*}
for any plaintext $m \in \mathbb{Z}_n$, and positive integer $k$.

This is trivially feasible if $m^2 \bmod n$ and $E(m^2 \bmod n)$ are known, since one can use the following equation to raise $m$ to any positive integer power.
\begin{align*}
	D(E(m^k)^{m^2 \bmod n}\bmod n^2) &= m^2m^k\bmod n \\
	&= m^{k+2}\bmod n
\end{align*}

We now show that including $m^2 \bmod n$ and $E(m^2 \bmod n)$ in a transmitted message does not compromise the security of the Paillier cryptosystem. Clearly, $E(m^2 \bmod n)$ can be shared without compromising security, as it is an encrypted quantity. The quantity $m^2 \bmod n$ does not expose the value of $m$ as finding the value of $m \bmod n$ given $m^2 \bmod n$ is a problem equivalent in hardness to the factorization of large integers \cite{crandall_prime_2005}.

@@

\subsubsection{Benaloh cryptosystem description}
We choose an integer $r$ and two large primes $p$ and $q$ such that the following conditions hold:
\begin{itemize}
  \item $r$ divides $(p-1)$;
  \item $\mathrm{gcd}(r,(p-1)/r)=1$;
  \item $\mathrm{gcd}(r,q-1)=1$.
\end{itemize}
Next, let $n=pq$ and $\phi = (p-1)(q-1)$, and choose $y\in \mathbb{Z}_n^* = \{ x \in \mathbb{Z}_n | \mathrm{gcd}(x,n)=1 \}$ such that the following conditions hold:
\begin{itemize}
  \item $y^{\phi/r}\neq 1 \bmod n$;
  \item For all prime factors $s$ of $r$, $y^{\phi/s}\neq 1 \bmod n$.
\end{itemize}
We denote the public key to be $(y,r,n)$ and the private key to be $(p,q)$.

@@

\subsubsection{Homomorphic Properties}
Similar to the Paillier cryptosystem, the Benaloh cryptosystem supports additive homomorphism as well as the multiplication of a plaintext scalar to an encrypted message.
For all $m_1,m_2 \in \mathbb{Z}_r$ and $k\in \mathbb{N}$, the following homomorphic properties hold.
\begin{description}
  \item[Additive homomorphism]
  \begin{align*}
    D(E(m_1)y^{m_2}\bmod n^2)=(m_1+m_2)\bmod n & \text{ (used to add a constant)}\\
    D(E(m_1)E(m_2)\bmod n^2)=(m_1+m_2)\bmod n & \text{ (used for binary addition)}
  \end{align*}
  \item[Multiplicative homomorphism]
  \begin{align*}
    D(E(m_1)^k\bmod n)= km_1\bmod n & \text{ (used to multiply a plaintext constant)}
  \end{align*}
\end{description}

@@

Similar to the Paillier cryptosystem, we can include $m^2$ and $E(m^2)$ in the transmitted message

>>>>

We will then show that the cryptosystems can be modified to support privacy-perserving polynomial evaluation in a client-server protocol: given an encrypted message $m$, evaluate $f(m)$ where $f$ is a polynomial function.

\subsection{The Pallier cryptosystem}
The Pallier cryptosystem \cite{stern_public-key_1999}, developed by Pascal Pallier, is a probabilistic encryption scheme which is based on the composite residuosity class problem. The scheme allows for the encryption and decryption of integer messages, and is known to be additively homomorphic. We now state the encryption and decryption algorithms of the Pallier cryptosystem and its homomorphic properties.

\subsubsection{Pallier Cryptosystem Description}
We first define a function $L(x)$ as the largest integer $v$ greater than zero such that $x-1 \geq vn$.
We choose two large primes $p$ and $q$, and set $n = pq, \lambda = \mathrm{lcm}(p-1,q-1)$.
Then we select an integer $g$, $0\leq g \leq n^2$ such that $\mathrm{gcd}(L(g^\lambda \bmod n^2), n) = 1$.
We denote the public key as $(g,n)$ and the private key $(p,q)$.

@@

\subsubsection{Homomorphic Properties of the Pailler Cryptosystem}
The Paillier cryptosystem supports additive homomorphism as well as the multiplication of a plaintext scalar to an encrypted message. These operations are defined as follows.
For all $m_1,m_2 \in \mathbb{Z}_n$ and $k\in \mathbb{N}$, the following homomorphic properties hold.
\begin{description}
  \item[Additive homomorphism]
  \begin{align*}
    D(E(m_1)g^k\bmod n^2)=(m_1+k)\bmod n & \text{ (used to add a constant)}\\
    D(E(m_1)E(m_2)\bmod n^2)=(m_1+m_2)\bmod n & \text{ (used for binary addition)}
  \end{align*}
  \item[Multiplicative homomorphism]
  \begin{align*}
    D(E(m_1)^k\bmod n^2)= km_1\bmod n & \text{ (used to multiply a plaintext constant)}
  \end{align*}
\end{description}
In order to implement some image operations covered in this study, we require the exponentiation of ciphertexts to integer powers, i.e. we require a function $f$ so that
\begin{align*}
	D(f(E(m))) = m^k\bmod n
\end{align*}
for any plaintext $m \in \mathbb{Z}_n$, and positive integer $k$.

%This is trivially feasible if $m^2 \bmod n$ and $E(m^2 \bmod n)$ are known, since one can use the following equation to raise $m$ to any positive integer power.
%\begin{align*}
%	D(E(m^k)^{m^2 \bmod n}\bmod n^2) &= m^2m^k\bmod n \\
%	&= m^{k+2}\bmod n
%\end{align*}

%We now show that including $m^2 \bmod n$ and $E(m^2 \bmod n)$ in a transmitted message does not compromise the security of the Paillier cryptosystem. Clearly, $E(m^2 \bmod n)$ can be shared without compromising security, as it is an encrypted quantity. The quantity $m^2 \bmod n$ does not expose the value of $m$ as finding the value of $m \bmod n$ given $m^2 \bmod n$ is a problem equivalent in hardness to the factorization of large integers \cite{crandall_prime_2005}.

@@

\subsubsection{Benaloh Cryptosystem Description}
We choose an integer $r$ and two large primes $p$ and $q$ such that the following conditions hold:
\begin{itemize}
  \item $r$ divides $(p-1)$;
  \item $\mathrm{gcd}(r,(p-1)/r)=1$;
  \item $\mathrm{gcd}(r,q-1)=1$.
\end{itemize}
Next, let $n=pq$ and $\phi = (p-1)(q-1)$, and choose $y\in \mathbb{Z}_n^* = \{ x \in \mathbb{Z}_n | \mathrm{gcd}(x,n)=1 \}$ such that the following conditions hold:
\begin{itemize}
  \item $y^{\phi/r}\neq 1 \bmod n$;
  \item For all prime factors $s$ of $r$, $y^{\phi/s}\neq 1 \bmod n$.
\end{itemize}
We denote the public key to be $(y,r,n)$ and the private key to be $(p,q)$.

@@

\subsubsection{Homomorphic Properties of the Benaloh Cryptosystem}
Similar to the Paillier cryptosystem, the Benaloh cryptosystem supports additive homomorphism as well as the multiplication of a plaintext scalar to an encrypted message.
For all $m_1,m_2 \in \mathbb{Z}_r$ and $k\in \mathbb{N}$, the following homomorphic properties hold.
\begin{description}
  \item[Additive homomorphism]
  \begin{align*}
    D(E(m_1)y^{m_2}\bmod n^2)=(m_1+m_2)\bmod n & \text{ (used to add a constant)}\\
    D(E(m_1)E(m_2)\bmod n^2)=(m_1+m_2)\bmod n & \text{ (used for binary addition)}
  \end{align*}
  \item[Multiplicative homomorphism]
  \begin{align*}
    D(E(m_1)^k\bmod n)= km_1\bmod n & \text{ (used to multiply a plaintext constant)}
  \end{align*}
\end{description}

@@

\section{General Exponentiation Protocol}
In order to perform polynomial evaluation, we first present a protocol for privacy-preserving exponentiation to a positive integer power, adapted from the protocol to calculate Euclidean distances used in \cite{hutchison_privacy-preserving_2009}.

The following protocols apply to both the Pailler and Benaloh cryptosystems, as they share similar homomorphisms.

Suppose Alice encrypts an integer $x$ and sends it so Bob has $E(x)$, and wants to obtain $E(x^2)$ without exposing the value of $x$.
\begin{itemize}
	\item Bob first selects a random integer $r$ and computes $E(x+r)$. Bob can do this since $r$ is a plaintext constant.
	\item Bob sends $E(x+r)$ to Alice, who decrypts the ciphertext to obtain $x+r$.
	\item Alice squares $x+r$ and encrypts the result. She sends $E((x+r)^2)$ to Bob.
	\item Bob computes $E(-2rx + r^2)$. He then computes $E((x+r)^2)E(-2rx + r^2) = E(x^2)$.
\end{itemize}

### 2018-10-05 parts/02_relatedliterature_06fullyhomomorphic.tex
Completed 3 of 4 cryptosystems
remaining cryptosystem is HeLib

\section{Fully homomorphic cryptosystems}
\subsection{Dasgupta-Pal cryptosystem}
The Dasgupta-Pal cryptosystem is a fully homomorphic cryptosystem proposed in 2016 by Smaranika Dasgupta and S. K. Pal \cite{dasgupta_design_2016}, which encrypts integer plaintexts in $\mathbb{Z}_n$ to polynomial ciphertexts. We begin our presentation of the Dasgupta-Pal cryptosystem with the following definition.

Given a message $m \in \mathbb{n}$, we denote
\begin{align*}
		m_p(x) = a_0 + a_1x + a_2x^2 + \cdots + a_kx^k
\end{align*}
where $a_ka_{k-1}\cdots a_2a_1_0$ is the binary representation of $m$.
\subsubsection{Dasgupta-Pal cryptosystem description}
Let $\ell$ denote the security parameter of the cryptosystem.
Let $S_k$ be a prime number with $\ell$ bits.
Choose a random even integer $z$ of length $\log_2{\ell}$.

@@

The scheme defines the encryption algorithm for a message $m \in \mathbb{Z}_n$ as follows:
\begin{align*}
	E(m) = y(x) + S_k\times d(x)
\end{align*}
where
$y(x)$ is a polynomial of degree $n$ such that $m_p(x) \equiv y(x) \bmod S_k$ and $d(x)$ is a randomly chosen polynomial of degree $n$.

@@

As a fully homomorphic cryptosystem, homomorphic operations on ciphertext introduce noise which may interfere with decryption.
To eliminate noise from a polynomial ciphertext, the following refresh function is used.
\begin{align*}
	R(c(x)) = c(x) \bmod R_k
\end{align*}

\subsubsection{Homomorphic properties}
It has been shown \cite{dasgupta_design_2016} that the following properties hold for all integer messages $m_1, m_2 \in \mathbb{Z}_n$ in the Dasgupta-Pal cryptosystem.
\begin{description}
  \item[Additive homomorphism]
  \begin{align*}
    D(E(m_1) + E(m_2))= m_1+m_2 & \text{ (used for binary addition)}
  \end{align*}
  \item[Multiplicative homomorphism]
  \begin{align*}
    D(E(m_1) \times E(m_2))= m_1 \times m_2 & \text{ (used for binary multiplication)}
  \end{align*}
\end{description}

\section{}

>>>>

\section{Fully Homomorphic Cryptosystems}
\subsection{Dasgupta-Pal Cryptosystem}
The Dasgupta-Pal cryptosystem is a fully homomorphic cryptosystem proposed in 2016 by Smaranika Dasgupta and S. K. Pal \cite{dasgupta_design_2016}, which encrypts integer plaintexts in $\mathbb{Z}_n$ to polynomial ciphertexts. We begin our presentation of the Dasgupta-Pal cryptosystem with the following definition.

Given a message $m \in \mathbb{n}$, we denote
\begin{align*}
		m_p(x) = a_0 + a_1x + a_2x^2 + \cdots + a_kx^k
\end{align*}
where $a_ka_{k-1}\cdots a_2a_1_0$ is the binary representation of $m$.

In the original scheme presented in \cite{dasgupta_design_2016}, the secret key $S_k$ is set to be a large prime. In Appendix \autoref{ch:correction}, we present a case where the Dasgupta-Pal cryptosystem fails and prove that setting the secret key $S_k = 2p$, where $p$ is a large prime, corrects errors in the Dasgupta-Pal cryptosystem.
We now decribe the correct cryptosystem.
\subsubsection{Corrected Dasgupta-Pal Cryptosystem Description}
Let $\ell$ denote the security parameter of the cryptosystem.
Let $S_k = 2p$, where $p$ is a prime number with $\ell - 1$ bits.
Choose a random even integer $z$ of length $\log_2{\ell}$.

@@

The scheme defines the encryption algorithm for a message $m$ as follows:
\begin{align*}
	E(m) = y(x) + S_k\times d(x)
\end{align*}
where
$y(x)$ is a polynomial of degree $n$ such that $m_p(x) \equiv y(x) \bmod S_k$ and $d(x)$ is a randomly chosen polynomial of degree $n$. This encrypts each coefficient of of $m_p(x)$ by adding some multiple of $S_k$ to it. Through this process, each bit of the message is encrypted separately.

@@

Dasgupta and Pal note that homomorphic operations on ciphertext introduce noise which may interfere with decryption, due to the potential increase in ciphertext values.
To eliminate noise from a polynomial ciphertext, the following refresh function is used.
\begin{align*}
	R(c(x)) = c(x) \bmod R_k
\end{align*}

\subsubsection{Homomorphic Properties of the Dasgupta-Pal Cryptosystem}
It has been shown \cite{dasgupta_design_2016} that the following properties hold for all integer messages $m_1, m_2 \in \mathbb{Z}_n$ in the Dasgupta-Pal cryptosystem. These properties arise since each coefficient in a ciphertext polynomial is essentially an independently encrypted bit of the original message.
\begin{description}
	\item[XOR on ciphertexts]
	An exclusive or (XOR) operation on integer messages can be achieved by adding the coefficients pairwise between two ciphertexts.
	\begin{align*}
		D(E(m_1)+E(m_2)) = m_1 \text{ XOR } m_2
	\end{align*}
	\item[AND on ciphertexts]
	Similarly, pair-wise multiplication of
	\begin{align*}
		D(E(a) \otimes E(b)) = a \text{ AND } b = ab \bmod 2
	\end{align*}
	where $\otimes$ denotes pairwise multiplication,
	\begin{align*}
		\sum_{i=1}^n{a_ix^i} \otimes \sum_{i=1}^n{b_ix^i} = \sum_{i=1}^n{a_ib_ix^i}.
	\end{align*}
\end{description}

### 2018-10-05 parts/08_appendices_a_cryptosystems.tex
Completed 3 of 4 cryptosystems
remaining cryptosystem is HeLib

%\section{Sample Questions for Different Studies}
%The following table presents three sample studies, as well as the guide questions that may help direct the discussion in each section of the paper. You may use this as another reference in writing your paper.
\chapter{DESCRIPTION OF CRYPTOSYSTEMS}

\section{Proof of the Correction Dasgupta-Pal Cryptosystem}
The Dasgupta-Pal cryptosystem encrypts each bit in a bit string independently.
In terms of single-bit encryption, the Dasgupta-Pal cryptosystem can be described as follows:
\begin{description}
	\item[Key generation]
	Let the secret key, $S_k$ be a large prime.
	Let the public refresh key, $R_k$, be $S_k \times z$, where $z$ is a large even integer.
	\item[Encryption]
	Given a message $m$, the encryption function is defined as
	\begin{align*}
		E(m) = m + S_kr
	\end{align*}
	where $r$ is a random integer.
	\item[Decryption]
	Given a ciphertext $c$, the decryption function is defined as
	\begin{align*}
		D(c) = c \bmod S_k \bmod 2
	\end{align*}
\end{description}
The homomorphic operations are then defined as
\begin{description}
	\item[XOR on ciphertexts]
	\begin{align*}
		D(E(a)+E(b)) = a \text{ XOR } b
	\end{align*}
	\item[AND on ciphertexts]
	\begin{align*}
		D(E(a)\times E(b)) = a \text{ AND } b
	\end{align*}
\end{description}
After repeated operations on ciphertexts, the resulting ciphertext can grow in magnitude.
To prevent storage issues and keep the ciphertext size small, a refresh function is used.
\begin{description}
	\item[Refresh function]
	Given a ciphertext $c$, the refresh function is defined as
	\begin{align*}
		R(c) = c \bmod R_k
	\end{align*}
\end{description}
\section{A Case Where Decryption Fails}
We consider the following quantity:
\begin{align}
	\label{eq:cornercase_ciphertext}
	D(\underbrace{E(1)+E(1)+\cdots+E(1)}_{S_k \text{ times}}).
\end{align}
Since $S_k$ is odd, the corresponding operation in the plaintext space is
\begin{align*}
	\label{eq:cornercase_plaintext}
	\underbrace{1 \text{ XOR } 1 \text{ XOR } \cdots \text{ XOR } 1}_{S_k \text{ times}} = 1.
\end{align*}
However, evaluating Equation \ref{eq:cornercase_ciphertext} yields:
\begin{align*}
	D(\underbrace{E(1)+E(1)+\cdots+E(1)}_{S_k \text{ times}})
	&= D\left(\sum_{i=1}^{S_k}{(1+S_kr_i)}\right)\\
	&= D\left(S_k + S_k\sum_{i=1}^{S_k}{r_i}\right)\\
	&= \left(S_k + S_k\sum_{i=1}^{S_k}{r_i}\right) \bmod S_k \bmod 2\\
	&= 0 \bmod 2\\
	&= 0.
\end{align*}
Since $1\neq 0$, we have shown an instance where incorrect decryption occurs given a sequence of operations on ciphertexts.
In general, a ciphertext in the Dasgupta-Pal cryptosystem is composed of a \textit{message-carrying addend} $A_m$ and a \textit{secret key addend} $A_s$ which is divisible by $S_k$. The message-carrying addend maintains the parity of the encoded bit, while the secret key addend obfuscates the message. This is maintained even when homomorphic operations are applied to ciphertexts:
\begin{align*}
	E(a) &= \underbrace{a}_{A_m} + \underbrace{S_kr}_{A_s}\\
	E(a)+E(b) &= (a + S_kr_1) + (b + S_kr_2)\\
	&= \underbrace{a+b}_{A_m} + \underbrace{S_k(r_1 + r_2)}_{A_s}\\
	E(a)\times E(b) &= (a + S_kr_1) \times (b + S_kr_2)\\
	&= \underbrace{ab}_{A_m} + \underbrace{S_k(br_1 + ar_2 + S_kr_1r_2)}_{A_s}
\end{align*}

Errors may occur in decryption when the message-carrying addend exceeds $S_k$.

The refresh function does not remedy this error: since $R_k > S_k$, refreshing the ciphertexts

\subsection{Correction to the Dasgupta-Pal Cryptosystem}
We now show that setting the secret key $S_k$ to $2p$, where $p$ is a prime, fixes the issue in the original cryptosystem.

>>>>

%\section{Sample Questions for Different Studies}
%The following table presents three sample studies, as well as the guide questions that may help direct the discussion in each section of the paper. You may use this as another reference in writing your paper.
\chapter{CORRECTION TO THE DASGUPTA-PAL CRYPTOSYSTEM}
\label{ch:correction}
\section{Bitwise Description of the Dasgupta-Pal Cryptosystem}
The Dasgupta-Pal cryptosystem \cite{dasgupta_design_2016} encrypts each bit in a bit string independently.
In terms of the encryption of a single bit, the Dasgupta-Pal cryptosystem can be described as follows:
\begin{description}
	\item[Key generation]
	Let the secret key, $S_k$ be a large prime.
	Let the public refresh key, $R_k$, be $S_k \times z$, where $z$ is a large even integer.
	\item[Encryption]
	Given a message $m$, the encryption function is defined as
	\begin{align*}
		E(m) = m + S_kr
	\end{align*}
	where $r$ is a random integer.
	\item[Decryption]
	Given a ciphertext $c$, the decryption function is defined as
	\begin{align*}
		D(c) = c \bmod S_k \bmod 2
	\end{align*}
\end{description}
The homomorphic operations are then defined as
\begin{description}
	\item[XOR on ciphertexts]
	\begin{align*}
		D(E(a)+E(b)) = a \text{ XOR } b = (a + b) \bmod 2
	\end{align*}
	\item[AND on ciphertexts]
	\begin{align*}
		D(E(a)\times E(b)) = a \text{ AND } b = ab \bmod 2
	\end{align*}
\end{description}
After repeated operations on ciphertexts, the resulting ciphertext can grow in magnitude.
To prevent storage issues and keep the ciphertext size small, a refresh function is used.
\begin{description}
	\item[Refresh function]
	Given a ciphertext $c$, the refresh function is defined as
	\begin{align*}
		R(c) = c \bmod R_k
	\end{align*}
\end{description}
\section{Cases Where Decryption Fails}
We consider the following quantity:
\begin{align}
	\label{eq:cornercase_ciphertext}
	D(\underbrace{E(1)+E(1)+\cdots+E(1)}_{S_k \text{ times}}).
\end{align}
Since $S_k$ is odd, the corresponding operation in the plaintext space is
\begin{align*}
	\label{eq:cornercase_plaintext}
	\underbrace{1 \text{ XOR } 1 \text{ XOR } \cdots \text{ XOR } 1}_{S_k \text{ times}} = 1.
\end{align*}
However, evaluating Equation \ref{eq:cornercase_ciphertext} yields:
\begin{align*}
	D(\underbrace{E(1)+E(1)+\cdots+E(1)}_{S_k \text{ times}})
	&= D\left(\sum_{i=1}^{S_k}{(1+S_kr_i)}\right)\\
	&= D\left(S_k + S_k\sum_{i=1}^{S_k}{r_i}\right)\\
	&= \left(S_k + S_k\sum_{i=1}^{S_k}{r_i}\right) \bmod S_k \bmod 2\\
	&= 0 \bmod 2\\
	&= 0.
\end{align*}
Since $\underbrace{1 \text{ XOR } 1 \text{ XOR } \cdots \text{ XOR } 1}_{S_k \text{ times}} = 1\neq 0 = D(\underbrace{E(1)+E(1)+\cdots+E(1)}_{S_k \text{ times}})$, we have shown an instance where incorrect decryption occurs given a sequence of operations on ciphertexts.

\subsection{Proposed Correction and Proof of Correctness}
We now show that setting the secret key $S_k$ to $2p$, where $p$ is a prime, fixes the issue in the original cryptosystem.
\begin{theorem}
	Suppose $S_k = 2p$, where $p$ is a prime. Then when addition or multiplication is performed between any two ciphertexts, correct decryption is assured.
\end{theorem}
\begin{proof}
	Suppose $c_1, c_2$ are two ciphertexts such that
	\begin{align*}
		c_1 = a + S_kr_1\\
		c_2 = b + S_kr_2
	\end{align*}
	We first consider addition. We want to show that $(c_1+c_2)\bmod S_k$ has the same parity as $a+b$.
	By the division algorithm, we have $a+b = S_kq + r$, for some $q,r$, $q \geq 0, r > 0$. We can rewrite $c_1+c_2$ as
	\begin{align*}
		c_1+c_2 &= (a + S_kr_1) + (b + S_kr_2)\\
		&= (a+b)+ S_k(r_1 + r_2)\\
		&= (S_kq + r) + S_k(r_1 + r_2)\\
		&= r + S_k(q + r_1 + r_2).
	\end{align*}
	Therefore $(c_1+c_2)\bmod S_k = r$.
	It is enough to show that the parity of $a+b$ is the same as the parity of $r$. We consider cases based on the parity of $a+b$.
	\begin{description}
		\item[Case 1: $a+b$ is odd.]
			Since $a+b = S_kq + r$, $S_kq + r$ must also be odd.
			$S_k$ is even, so $S_kq$ is also even.
			For $S_kq + r$ to be odd, $r$ must be odd, since $S_k$ is even.

			Therefore, the parity of $a+b$ is the same as the parity of $r$.
		\item[Case 2: $a+b$ is even.]
			Since $a+b = S_kq + r$, $S_kq + r$ must also be even.
			$S_k$ is even, so $S_kq$ is also even. For $S_kq + r$ to be even, $r$ must be even , since $S_k$ is even.

			Therefore, the parity of $a+b$ is the same as the parity of $r$.
	\end{description}
	Therefore correct decryption is assured for the sum of ciphertexts.

	We now consider multiplication. We want to show that $c_1c_2 \bmod S_k$ has the same parity as $ab$. Similar to the addition case, by the division algorithm, we can write $ab = S_kq + r$, $q > 0, r > 0$ for some $q,r$. We can rewrite $c_1c_2$ as
	\begin{align*}
		c_1c_2 &= (a + S_kr_1) \times (b + S_kr_2)\\
		&= ab + S_k(br_1 + ar_2 + S_kr_1r_2)\\
		&= (S_kq + r) + S_k(br_1 + ar_2 + S_kr_1r_2)\\
		&= r + S_k(q + br_1 + ar_2 + S_kr_1r_2).
	\end{align*}
	Therefore $c_1c_2 \bmod S_k = r$.
	It is enough to show that the parity of $ab$ is the same as the parity of $r$. We consider cases based on the parity of $ab$.
	\begin{description}
		\item[Case 1: $ab$ is odd.]
			Since $ab = S_kq + r$, $S_kq + r$ must also be odd.
			$S_k$ is even, so $S_kq$ is also even.
			For $S_kq + r$ to be odd, $r$ must be odd, since $S_k$ is even.

			Therefore, the parity of $a+b$ is the same as the parity of $r$.
		\item[Case 2: $ab$ is even.]
			Since $ab = S_kq + r$, $S_kq + r$ must also be even.
			$S_k$ is even, so $S_kq$ is also even. For $S_kq + r$ to be even, $r$ must be even , since $S_k$ is even.

			Therefore, the parity of $ab$ is the same as the parity of $r$.
	\end{description}
	Therefore, correct decryption is assured for both addition and multiplication of ciphertexts.
\end{proof}
